Reanalysis Step 5: Outcome Analysis with Three-Way Interaction

### 2025-09-01 reanalysis-5-outcome_analysis-interaction.qmd
dont cache

  # Initialize pooled results data frames
  pooled_or_results <- data.frame(
    dr_severity = first_contrast$dr_severity,
    any_treatment = first_contrast$any_treatment,
    contrast = first_contrast$contrast,
    log_odds = numeric(n_subgroups),
    SE_log_odds = numeric(n_subgroups),
    df = numeric(n_subgroups),
    stringsAsFactors = FALSE
  )

  pooled_rd_results <- data.frame(
    dr_severity = first_rd$dr_severity,
    any_treatment = first_rd$any_treatment,
    contrast = first_rd$contrast,
    risk_diff = numeric(n_subgroups),
    SE_risk_diff = numeric(n_subgroups),
    df = numeric(n_subgroups),
    stringsAsFactors = FALSE
  )

@@

  # Pool each subgroup using Rubin's rules
  for (j in 1:n_subgroups) {
    # Pool odds ratio contrasts (log scale)
    log_odds_estimates <- sapply(all_contrasts, function(x) {
      if ("estimate" %in% names(x)) {
        x$estimate[j]
      } else {
        # Try other possible column names
        x[j, which(names(x) %in% c("estimate", "emmean", "contrast"))[1]]
      }
    })

    log_odds_SEs <- sapply(all_contrasts, function(x) {
      if ("SE" %in% names(x)) {
        x$SE[j]
      } else if ("std.error" %in% names(x)) {
        x$std.error[j]
      } else {
        x[j, which(names(x) %in% c("SE", "std.error", "se"))[1]]
      }
    })

@@

    # Pool risk differences (probability scale)
    # Check for column names - emmeans may use 'estimate' or other names
    rd_estimates <- sapply(all_risk_diffs, function(x) {
      if ("estimate" %in% names(x)) {
        x$estimate[j]
      } else if ("emmean" %in% names(x)) {
        x$emmean[j]
      } else if ("prob" %in% names(x)) {
        x$prob[j]
      } else {
        # Try to get the estimate column (might be named differently)
        x[j, which(names(x) %in% c("estimate", "emmean", "prob", "prediction"))[1]]
      }
    })

    rd_SEs <- sapply(all_risk_diffs, function(x) {
      if ("SE" %in% names(x)) {
        x$SE[j]
      } else if ("std.error" %in% names(x)) {
        x$std.error[j]
      } else {
        # Try to get the SE column
        x[j, which(names(x) %in% c("SE", "std.error", "se"))[1]]
      }
    })

>>>>

  # Initialize pooled results data frames
  pooled_or_results <- data.frame(
    dr_severity = first_contrast$dr_severity,
    any_treatment = first_contrast$any_treatment,
    contrast = first_contrast$contrast,
    log_odds = as.numeric(n_subgroups),
    SE_log_odds = as.numeric(n_subgroups),
    df = as.numeric(n_subgroups),
    stringsAsFactors = FALSE
  )

  pooled_rd_results <- data.frame(
    dr_severity = first_rd$dr_severity,
    any_treatment = first_rd$any_treatment,
    contrast = first_rd$contrast,
    risk_diff = as.numeric(n_subgroups),
    SE_risk_diff = as.numeric(n_subgroups),
    df = as.numeric(n_subgroups),
    stringsAsFactors = FALSE
  )

@@

  # Pool each subgroup using Rubin's rules
  for (j in 1:n_subgroups) {
    # Pool odds ratio contrasts (log scale)
    # Extract the j-th estimate from each imputation
    log_odds_estimates <- sapply(all_contrasts, function(x) {
      x$estimate[j]
    })

    log_odds_SEs <- sapply(all_contrasts, function(x) {
      x$SE[j]
    })

@@

    # Pool risk differences (probability scale)
    # Extract the j-th estimate from each imputation
    rd_estimates <- sapply(all_risk_diffs, function(x) {
      x$estimate[j]
    })

    rd_SEs <- sapply(all_risk_diffs, function(x) {
      x$SE[j]
    })
